---
title: "Automatic Cross Validation model for M3 Competition data"
author: 'Poon, Athit Srimachand'
output:
  html_document:
    theme: paper
    highlight: pygments
    toc_float: yes
    toc: yes
---

```{r library, include = FALSE}
lapply(c("tidyverse", "dplyr", "gridExtra", "data.table", "lubridate", # general purpose packages
         "Mcomp","forecast", "tseries", # forecast packages and data sets
         "foreach", "doSNOW","doParallel"), # Packages for run code with many cores simultaneously
        library, character.only = TRUE)
```

# Part 2: Batch Forecasting

## 1. Data Extraction and prepare statistics function

```{r , echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results='hide'}

# 1.1 Create data frame to gather the information of each ts and Explore

info_series <-  data.frame(matrix(NA, ncol = 8, nrow = 130))
colnames(info_series) <- c("series", "type", "length.in", "mean", "min", "max", "IQR", "sd")
for (i in 1:130){
  s_count <- 1508 + (i-1)*10
  info_series[i,1] <- s_count 
  info_series[i,2] <- M3[[s_count]]$type
  info_series[i,3] <- length(M3[[s_count]]$x)
  info_series[i,4] <- mean(M3[[s_count]]$x)
  info_series[i,5] <- min(M3[[s_count]]$x)
  info_series[i,6] <- max(M3[[s_count]]$x)
  info_series[i,7] <- IQR(M3[[s_count]]$x)
  info_series[i,8] <- sd(M3[[s_count]]$x)
}
mean(info_series$max);mean(info_series$min);mean(info_series$sd);mean(info_series$mean)
mean(info_series$length.in); sd(info_series$length.in)
# from skimming time series: all data of ts are positive and much greater than 0
# they can have different scale of unit and from different industries
# this suggests MAPE as the error measure to determine the model selection in CV

#-------------------------------------------------------------------------------
# 1.2 Generate error measure functions

# functions to produce error measure function
MAE <- function(y_pred, y_out){MLmetrics:::MAE(y_pred, y_out)}
AE <- function(y_pred, y_out) {return(abs(y_out - y_pred))}
RAE <- function(y_pred, y_out, y_bench, epsilon = 0.0001) {
  return(abs(y_pred - y_out)/(abs(y_bench - y_out) + epsilon))}
gmean <- function(x, na.rm = TRUE) {exp(sum(base::log(x[x > 0]), na.rm = na.rm) / length(x))}

# error measures
MAPE <- function(y_pred, y_out){round(MLmetrics:::MAPE(y_pred, y_out)*100, digits = 3)}
MdAPE <- function(y_pred, y_out){round(MLmetrics:::MedianAPE(y_pred, y_out)*100, digits = 3)}
sMAPE <- function(y_pred, y_out){round(Metrics:::smape(y_out, y_pred)*100, digits = 3)}
MASE <- function(y_pred, y_out, y_in){round(ftsa:::error(forecast = y_pred,true = y_out,
                                                          insampletrue = y_in, method = "mase"), digits = 3)}
GMRAE <- function(y_pred, y_out, y_bench){round(gmean(RAE(y_out = y_out, y_pred = y_pred, y_bench = y_bench)), digits = 3)}
RelMAE <- function(y_pred, y_out, y_bench){round(MAE(y_pred, y_out)/MAE(y_bench, y_out), digits = 3)}

# test:
# y_in <- M3[[1998]]$x
# y_out <- M3[[1998]]$xx
# y_bench <- naive(y_in, h = 18)$mean
# fit <- Arima(y_in, order=c(1, 0, 1), seasonal=c(0, 1, 1), method="CSS")
# y_pred <- forecast(fit, h = 18)$mean
# 
# MAPE(y_pred, y_out)
# MdAPE(y_pred, y_out)
# sMAPE(y_pred, y_out)
# MASE(y_pred, y_out, y_in)
# GMRAE(y_pred, y_out, y_bench)
# RelMAE(y_pred, y_out, y_bench)
```

## 2. Prepare functions for cross validation

```{r , echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results='hide'}

# 2.1 CV function for separating training and validation data set from in-sample

sep_ts <- function(ts, min.train.size, v.len, current.step){
  yt <<- window(ts, start = time(ts)[1], end = time(ts)[min.train.size + current.step - 1])
  yv <<- window(ts, start = time(ts)[min.train.size + current.step], end = time(ts)[min.train.size + current.step + v.len - 1])
}

# test:
#sep_ts(M3[[1908]]$x,72,18,2); yt; yv

#-------------------------------------------------------------------------------

# 2.2 CV function to retrieve MAPE of ETS and ARIMA models

MAPE_ets <- function(yt, yv, model, damp){
  fit <- ets(yt, model = model, damped = damp)
  fcs <- forecast(fit, h = length(yv))$mean
  #return(MLmetrics:::MAPE(fcs, yv))
  return(MAPE(fcs, yv))}

MAPE_ari <- function(yt, yv, ari.p, ari.d, ari.q, ari.P, ari.D, ari.Q){
  fit <- Arima(yt, order=c(ari.p, ari.d, ari.q), seasonal=c(ari.P, ari.D, ari.Q), method="CSS")
  fcs <- forecast(fit, h = length(yv))$mean
  #return(MLmetrics:::MAPE(fcs, yv))
  return(MAPE(fcs, yv))}

# test:
# sep_ts(M3[[1908]]$x,72,18,2); yt; yv; MAPE_ari(yt, yv, 1, 0, 1, 0, 1, 1); MAPE_ets(yt, yv, "ANA", FALSE)
```

## 3. Cross Validation

```{r , echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results='hide'}

# 3.1 Create main table and temp table to gather result of cross validations
# create temp file to use in foreach() loop
cv_dt_temp <-  data.table(
  series      = 0,
  type        = "",
  length.in   = 0,
  cv.step.no  = 0,
  ets.cv.MAPE = 0,
  ari.cv.MAPE = 0,
  ets.model   = "",
  ets.e       = "",
  ets.t       = "",
  ets.s       = "",
  ets.damp    = FALSE,
  ari.p       = 0,
  ari.d       = 0,
  ari.q       = 0,
  ari.P       = 0,
  ari.D       = 0,
  ari.Q       = 0,
  ari.s       = 0)
cv_dt <- cv_dt_temp[0]

#-------------------------------------------------------------------------------
# 3.2 Cross validation (run time approx = 150 sec)

# 3.2.1 Prepare parallel calculation and timer
cl <- makeCluster(detectCores()-1)
registerDoSNOW(cl)
iterations <- 130
pb <- txtProgressBar(max = iterations, style = 3)
progress <- function(n){setTxtProgressBar(pb, n)}
opts <- list(progress = progress)
ptm <- proc.time()

# 3.2.2 Start for loop for cross validation with the result inputting in cv_dt table
cv_dt <- foreach(i = 1:iterations, .combine = rbind, .options.snow = opts) %dopar% {
  library(Mcomp)
  library(forecast)
  s_count <- 1508 + (i-1)*10
  ts <- M3[[s_count]]$x
  cv_dt_temp$series <- s_count 
  cv_dt_temp$type <- M3[[s_count]]$type
  cv_dt_temp$length.in <- length(M3[[s_count]]$x)
  #---------------------------------------------------------------
  # 3.2.3 fit auto ets to find fitting parameters
  ets.comp <- ets(ts, model = "ZZZ")$components
  cv_dt_temp$ets.e <- ets.comp[1]
  cv_dt_temp$ets.t <- ets.comp[2]
  cv_dt_temp$ets.s<- ets.comp[3]
  cv_dt_temp$ets.damp <- as.logical(ets.comp[4])
  cv_dt_temp$ets.model <- paste(ets.comp[1], ets.comp[2], ets.comp[3], sep="")
  #---------------------------------------------------------------
  # 3.2.4 fit auto arima to find fitting parameters
  ari.comp <- auto.arima(ts)$arma
  cv_dt_temp$ari.p <- ari.comp[1]
  cv_dt_temp$ari.d <- ari.comp[6]
  cv_dt_temp$ari.q <- ari.comp[2]
  cv_dt_temp$ari.P <- ari.comp[3]
  cv_dt_temp$ari.D <- ari.comp[7]
  cv_dt_temp$ari.Q <- ari.comp[4]
  cv_dt_temp$ari.s <- ari.comp[5]
  #---------------------------------------------------------------
  # 3.2.5 Prepare parameters for Cross validation
  v.len <- 18 
  min.train.size <- v.len * 4 
  total.step <- length(ts) - (min.train.size + v.len - 1)
  if (total.step < 12){
    total.step <- 6
    min.train.size <- length(ts) - (total.step + v.len - 1)
  } else if (total.step >= 12 && total.step < 24) {
    total.step <- 12
    min.train.size <- length(ts) - (total.step + v.len - 1)
  } else if (total.step >= 24 && total.step < 36) {
    total.step <- 24
    min.train.size <- length(ts) - (total.step + v.len - 1)
  } else if (total.step >= 36 && total.step < 48) {
    total.step <- 36
    min.train.size <- length(ts) - (total.step + v.len - 1)
  } else if (total.step >= 48 && total.step < 60) {
    total.step <- 48
    min.train.size <- length(ts) - (total.step + v.len - 1)
  } else if (total.step >= 60 && total.step < 72) {
    total.step <- 60
    min.train.size <- length(ts) - (total.step + v.len - 1)
  } else {
    total.step <- 72
    min.train.size <- length(ts) - (total.step + v.len - 1)
  }
  #---------------------------------------------------------------
  # 3.2.6 Prepare parameters to store MAPEs df from a loop
  
  # MAPE in each rolling cross validation stored in MAPEs data frame
  MAPEs <- data.frame(matrix(NA, ncol = 2, nrow = total.step))
  colnames(MAPEs) <- c("MAPE_ets", "MAPE_ari")
  #---------------------------------------------------------------
  # 3.2.7 a loop of rolling cross validation (number of loops = total.step)
  for (current.step in 1:total.step){
    sep_ts(ts, min.train.size, v.len, current.step)
    MAPEs$MAPE_ets[current.step] <- MAPE_ets(yt, yv, cv_dt_temp$ets.model, cv_dt_temp$ets.damp)
    MAPEs$MAPE_ari[current.step] <- MAPE_ari(yt, yv, cv_dt_temp$ari.p, cv_dt_temp$ari.d, cv_dt_temp$ari.q,
                                cv_dt_temp$ari.P, cv_dt_temp$ari.D, cv_dt_temp$ari.Q)
  }
  #---------------------------------------------------------------
  # 3.2.8 assign mean of MAPEs and number of rolling steps to cv_dt_temp data table
  cv_dt_temp$ets.cv.MAPE <- mean(MAPEs$MAPE_ets)
  cv_dt_temp$ari.cv.MAPE <- mean(MAPEs$MAPE_ari)
  cv_dt_temp$cv.step.no <- length(MAPEs$MAPE_ari)
  #---------------------------------------------------------------
  # 3.2.9 rbind cv_dt_temp to cv_dt
  return(cv_dt_temp)
}
proc.time() - ptm
stopCluster(cl)

#-------------------------------------------------------------------------------
# 3.3 Create new data frame based on data table for evaluation
# define col select.flag which = 1 when ets is selected and = 0 when arima is selected
cv_df <- tibble(cv_dt)
cv_df <- cv_df %>% mutate(select.flag = ifelse(ets.cv.MAPE < ari.cv.MAPE, 1, 0))
```

## 4. Prepare functions and parameters for error evaluation

```{r , echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results='hide'}

# 4.1 Define parameters for different accuracy measures,  horizons, models
error_list <- c("MAPE", "MdAPE", "MASE", "GMRAE", "RelMAE")
horizon.list <- 1:18
model.list <- c("auto.ets", "auto.ari", "model.select", "naive", "ets.damp", "seasonal.naive")
#-------------------------------------------------------------------------------
# 4.2 function to retrieve the result of error measures from predicted y and input y
error_meas <- function(y_pred, y_out, y_bench, y_in){
  output <- data.frame(matrix(0, nrow = 1, ncol = 5))
  colnames(output) <- error_list
  output$MAPE <- MAPE(y_pred, y_out)
  output$MdAPE <- MdAPE(y_pred, y_out)
  output$MASE <- MASE(y_pred, y_out, y_in)
  output$GMRAE <- GMRAE(y_pred, y_out, y_bench)
  output$RelMAE <- RelMAE(y_pred, y_out, y_bench)
  return(output)
}
#-------------------------------------------------------------------------------
# 4.3 function to forecast and retrieve error measures
fcs_error <- function(fit = 0, y_in, y_out, model, horizon){
  # must input fit for "auto.ets", "auto.ari", "model.select", "ets.damp"
  if (model == "naive"){
    y_pred <- naive(y_in, h = horizon)$mean
  } else if (model == "seasonal.naive"){
    y_pred <- snaive(y_in, h = horizon)$mean
  } else if (model %in% c("auto.ets", "auto.ari", "model.select", "ets.damp")){
    y_pred <- forecast(fit, h = horizon)$mean
  }
  y_out <- y_out[1:horizon]
  y_bench <- naive(y_in, h = horizon)$mean
  return(error_meas(y_pred, y_out, y_bench, y_in))
}
#-------------------------------------------------------------------------------
# test:
# fit <- Arima(M3[[1998]]$x, order=c(1, 0, 1), seasonal=c(0, 1, 1), method="CSS")
# horizon <- 18
# y_out <- M3[[1998]]$xx
# y_in <- M3[[1998]]$x
# fcs_error(fit, y_in, y_out, "auto.ari", horizon)
```

## 5. Find forecast accuracy

```{r , echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results='hide'}

# 5.1 Create main and temp df to gather result of forecast accuracy

# Define temp df for foreach loop
eva_temp <- data.frame(matrix(NA, ncol = 14, nrow = 1))
colnames(eva_temp) <- c("series", "type", "length.in", "cv.step.no", "ets.t", "ets.s", "ets.damp", "horizon",
                               "model", "MAPE", "MdAPE", "MASE", "GMRAE", "RelMAE")

# Define the main data frame that collects all result
eva_df <- data.frame(matrix(NA, ncol = length(eva_temp), nrow = 0)); colnames(eva_df) <- colnames(eva_temp)
#-------------------------------------------------------------------------------
# 5.2 Find forecast accuracy (run time approx 17 sec)

# 5.2.1 Prepare parallel calculation and timer
cl <- makeCluster(detectCores()-1)
registerDoSNOW(cl)
iterations <- 130
pb <- txtProgressBar(max = iterations, style = 3)
progress <- function(n){setTxtProgressBar(pb, n)}
opts <- list(progress = progress)
ptm <- proc.time()
#-------------------------------------------------------------------------------
# 5.2.2 Proceed the calculation of error measures per (model, horizon)
eva_df <- foreach(i = 1:iterations, .combine = rbind, .options.snow = opts) %dopar% {
  library(Mcomp)
  library(forecast)
  eva_df_temp <- data.frame(matrix(NA, ncol = length(eva_temp), nrow = 0)); colnames(eva_df) <- colnames(eva_temp)
  s_count <- 1508 + (i-1)*10 # + 10
  y_in <- M3[[s_count]]$x
  y_out <- M3[[s_count]]$xx
  #-----------------------------------------------------------------------------
  # 5.2.3 fit necessary models for producing forecast
  fit <- list(auto.ets = 0, auto.ari = 0, model.select = 0, naive = 0, ets.damp = 0, seasonal.naive = 0)
  # auto.ets
  fit$auto.ets <- ets(y_in, model = cv_df$ets.model[i], damped = cv_df$ets.damp[i])
  # auto.ari
  fit$auto.ari <- Arima(y_in, order=c(cv_df$ari.p[i], cv_df$ari.d[i], cv_df$ari.q[i]), 
               seasonal=c(cv_df$ari.P[i], cv_df$ari.D[i], cv_df$ari.Q[i]), method="CSS")
  # model.select
  if (cv_df$select.flag[i] == 1){
    fit$model.select <- ets(y_in, model = cv_df$ets.model[i], damped = cv_df$ets.damp[i])
  } else if (cv_df$select.flag[i] == 0) {
    fit$model.select <- Arima(y_in, order=c(cv_df$ari.p[i], cv_df$ari.d[i], cv_df$ari.q[i]), 
               seasonal=c(cv_df$ari.P[i], cv_df$ari.D[i], cv_df$ari.Q[i]), method="CSS")
  }
  # ets.damp
  fit$ets.damp <- ets(y_in, model = "AAN", damped = TRUE)
  # it is unnecessary to fit naive and seasonal naive 
  #-----------------------------------------------------------------------------
  # 5.2.4 for loop to run and retrieve error measurement results
   
  # loop per horizon : horizon.list <- 1:18
  for (j in 1:length(horizon.list)){
    # loop per model : model.list <- c("auto.ets", "auto.ari", "model.select", "naive", "ets.damp", "seasonal.naive")
    for (k in 1:length(model.list)){
      
      # run defined function - fcs_error() and stored in temp_error
      temp_error <- fcs_error(fit[[k]], y_in, y_out, model.list[k], horizon.list[j])
      
      # store data for every column in eva_temp df
      eva_temp$series     <- cv_df$series[i]
      eva_temp$type       <- cv_df$type[i]
      eva_temp$length.in  <- cv_df$length.in[i]
      eva_temp$cv.step.no <- cv_df$cv.step.no[i]
      eva_temp$ets.t      <- cv_df$ets.t[i]
      eva_temp$ets.s      <- cv_df$ets.s[i]
      eva_temp$ets.damp   <- cv_df$ets.damp[i]
      eva_temp$horizon    <- horizon.list[j]
      eva_temp$model      <- model.list[k]
      eva_temp$MAPE       <- temp_error$MAPE
      eva_temp$MdAPE      <- temp_error$MdAPE
      eva_temp$MASE       <- temp_error$MASE
      eva_temp$GMRAE      <- temp_error$GMRAE
      eva_temp$RelMAE     <- temp_error$RelMAE
      
      # rbind 1 row of eva_temp to main temp df (eva_df_temp) for rbind logic in foreach
      eva_df_temp <- rbind(eva_df_temp, eva_temp)
    }
  }
  # rbind logic in foreach
  return(eva_df_temp)
}
stopCluster(cl)
proc.time() - ptm

```

## 6. Data analysis and Visualisation

### 6.1 Test filter: to confirm the correctness of the error evaluation code

```{r , echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results='hide'}
# 108 row per series = 6 * 18
eva_df %>% filter(series %in% c(1508))
nrow(eva_df %>% filter(series %in% c(1508)))
#-------------------------------------------------------------------------------
# 18 row per model - series
eva_df %>% filter(model == "model.select", series %in% c(1508))
nrow(eva_df %>% filter(model == "model.select", series %in% c(1508)))
#-------------------------------------------------------------------------------
# 6 row per horizon -  series
eva_df %>% filter(horizon == 18, series %in% c(1508))
nrow(eva_df %>% filter(horizon == 18, series %in% c(1508)))
#-------------------------------------------------------------------------------
# 1 row per horizon - model - series
eva_df %>% filter(horizon == 18, model == "model.select", series %in% c(1508))
```

### 6.2 How is the accuracy for each 1.model 2.horizon 3.measure ?

```{r , echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}

acc_all <- eva_df %>%
  group_by(model) %>%
  summarise(mean(MAPE), mean(MdAPE), gmean(RelMAE), gmean(MASE)) %>%
  ungroup()
acc_all
#-------------------------------------------------------------------------------
acc_short <- eva_df %>%
  filter(horizon %in% 1:6) %>%
  group_by(model) %>%
  summarise(mean(MAPE), mean(MdAPE), gmean(RelMAE), gmean(MASE)) %>%
  ungroup()
acc_short
#-------------------------------------------------------------------------------
acc_medium <- eva_df %>%
  filter(horizon %in% 7:12) %>%
  group_by(model) %>%
  summarise(mean(MAPE), mean(MdAPE), gmean(RelMAE), gmean(MASE)) %>%
  ungroup()
acc_medium 
#-------------------------------------------------------------------------------
acc_long <- eva_df %>%
  filter(horizon %in% 13:18) %>%
  group_by(model) %>%
  summarise(mean(MAPE), mean(MdAPE), gmean(RelMAE), gmean(MASE)) %>%
  ungroup()
acc_long
```

### 6.3 Which model is the best in each 1.type 2.horizon 3.measure ?

```{r , echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
type <- eva_df %>% dplyr:::select(type) %>% distinct()
type <- c("MICRO", "INDUSTRY", "MACRO", "FINANCE", "DEMOGRAPHIC", "OTHER")
best <- data.frame(matrix(NA, nrow = 4, ncol = 7))
rownames(best) <- c("All (t+1 to t+18)", "Short (t+1 to t+6)", "Medium (t+7 to t+12)", "Long (t+13 to t+18)")
colnames(best) <- c("MICRO", "INDUSTRY", "MACRO", "FINANCE", "DEMOGRAPHIC", "OTHER", "ALL")
#-------------------------------------------------------------------------------
acc_all_type <- eva_df %>%
  group_by(model, type) %>%
  summarise(mean(MAPE), mean(MdAPE), gmean(MASE), gmean(GMRAE), gmean(RelMAE)) %>%
  ungroup()
acc_short_type <- eva_df %>%
  filter(horizon %in% 1:6) %>%
  group_by(model, type) %>%
  summarise(mean(MAPE), mean(MdAPE), gmean(MASE), gmean(GMRAE), gmean(RelMAE)) %>%
  ungroup()
acc_medium_type <- eva_df %>%
  filter(horizon %in% 7:12) %>%
  group_by(model, type) %>%
  summarise(mean(MAPE), mean(MdAPE), gmean(MASE), gmean(GMRAE), gmean(RelMAE)) %>%
  ungroup()
acc_long_type <- eva_df %>%
  filter(horizon %in% 13:18) %>%
  group_by(model, type) %>%
  summarise(mean(MAPE), mean(MdAPE), gmean(MASE), gmean(GMRAE), gmean(RelMAE)) %>%
  ungroup()
#-------------------------------------------------------------------------------
# number of series per type
info_series %>% group_by(type) %>% summarise(n())
# 1 DEMOGRAPHIC    11
# 2 FINANCE        14
# 3 INDUSTRY       34
# 4 MACRO          31
# 5 MICRO          37
# 6 OTHER           3
#-------------------------------------------------------------------------------
# Best AvgRelMAE
best_AvgRelMAE <- best
# for loop per type (6 types)
for (i in 1:6) {
  best_AvgRelMAE[1,i] <- (acc_all_type %>% filter(type == type[i]) %>% top_n(-1, `gmean(RelMAE)`))$model
  best_AvgRelMAE[2,i] <- (acc_short_type %>% filter(type == type[i]) %>% top_n(-1, `gmean(RelMAE)`))$model
  best_AvgRelMAE[3,i] <- (acc_medium_type %>% filter(type == type[i]) %>% top_n(-1, `gmean(RelMAE)`))$model
  best_AvgRelMAE[4,i] <- (acc_long_type %>% filter(type == type[i]) %>% top_n(-1, `gmean(RelMAE)`))$model
}
best_AvgRelMAE$ALL[1] <- (acc_all %>% top_n(-1, `gmean(RelMAE)`))$model
best_AvgRelMAE$ALL[2] <- (acc_short %>% top_n(-1, `gmean(RelMAE)`))$model
best_AvgRelMAE$ALL[3] <- (acc_medium %>% top_n(-1, `gmean(RelMAE)`))$model
best_AvgRelMAE$ALL[4] <- (acc_long %>% top_n(-1, `gmean(RelMAE)`))$model
best_AvgRelMAE
#-------------------------------------------------------------------------------
# Best MASE
best_MASE<- best
# for loop per type (6 types)
for (i in 1:6) {
  best_MASE[1,i] <- (acc_all_type %>% filter(type == type[i]) %>% top_n(-1, `gmean(MASE)`))$model
  best_MASE[2,i] <- (acc_short_type %>% filter(type == type[i]) %>% top_n(-1, `gmean(MASE)`))$model
  best_MASE[3,i] <- (acc_medium_type %>% filter(type == type[i]) %>% top_n(-1, `gmean(MASE)`))$model
  best_MASE[4,i] <- (acc_long_type %>% filter(type == type[i]) %>% top_n(-1, `gmean(MASE)`))$model
}
best_MASE$ALL[1] <- (acc_all %>% top_n(-1, `gmean(MASE)`))$model
best_MASE$ALL[2] <- (acc_short %>% top_n(-1, `gmean(MASE)`))$model
best_MASE$ALL[3] <- (acc_medium %>% top_n(-1, `gmean(MASE)`))$model
best_MASE$ALL[4] <- (acc_long %>% top_n(-1, `gmean(MASE)`))$model
best_MASE
#-------------------------------------------------------------------------------
# Best MdAPE
best_MdAPE <- best
# for loop per type (6 types)
for (i in 1:6) {
  best_MdAPE[1,i] <- (acc_all_type %>% filter(type == type[i]) %>% top_n(-1, `mean(MdAPE)`))$model
  best_MdAPE[2,i] <- (acc_short_type %>% filter(type == type[i]) %>% top_n(-1, `mean(MdAPE)`))$model
  best_MdAPE[3,i] <- (acc_medium_type %>% filter(type == type[i]) %>% top_n(-1, `mean(MdAPE)`))$model
  best_MdAPE[4,i] <- (acc_long_type %>% filter(type == type[i]) %>% top_n(-1, `mean(MdAPE)`))$model
}
best_MdAPE$ALL[1] <- (acc_all %>% top_n(-1, `mean(MdAPE)`))$model
best_MdAPE$ALL[2] <- (acc_short %>% top_n(-1, `mean(MdAPE)`))$model
best_MdAPE$ALL[3] <- (acc_medium %>% top_n(-1, `mean(MdAPE)`))$model
best_MdAPE$ALL[4] <- (acc_long %>% top_n(-1, `mean(MdAPE)`))$model
best_MdAPE
#-------------------------------------------------------------------------------
# Best MAPE
best_MAPE<- best
# for loop per type (6 types)
for (i in 1:6) {
  best_MAPE[1,i] <- (acc_all_type %>% filter(type == type[i]) %>% top_n(-1, `mean(MAPE)`))$model
  best_MAPE[2,i] <- (acc_short_type %>% filter(type == type[i]) %>% top_n(-1, `mean(MAPE)`))$model
  best_MAPE[3,i] <- (acc_medium_type %>% filter(type == type[i]) %>% top_n(-1, `mean(MAPE)`))$model
  best_MAPE[4,i] <- (acc_long_type %>% filter(type == type[i]) %>% top_n(-1, `mean(MAPE)`))$model
}
best_MAPE$ALL[1] <- (acc_all %>% top_n(-1, `mean(MAPE)`))$model
best_MAPE$ALL[2] <- (acc_short %>% top_n(-1, `mean(MAPE)`))$model
best_MAPE$ALL[3] <- (acc_medium %>% top_n(-1, `mean(MAPE)`))$model
best_MAPE$ALL[4] <- (acc_long %>% top_n(-1, `mean(MAPE)`))$model
best_MAPE
```

### 6.4 Best in each season and trend / MASE in each season and trend ?

```{r , echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
season <- c("A", "M", "N")
st_best <- data.frame(matrix(NA, nrow = 3, ncol = 3))
rownames(st_best) <- c("Additive", "Multiplicative", "None") # season
colnames(st_best) <- c("Additive", "Damped", "None") # trend
st_acc <- data.frame(matrix(NA, nrow = 3, ncol = 3))
rownames(st_acc) <- c("Additive", "Multiplicative", "None")
colnames(st_acc) <- c("Additive", "Damped", "None")
#-------------------------------------------------------------------------------
st_eva <- eva_df %>%
  group_by(ets.t, ets.damp, ets.s, model) %>%
  summarize(gmean(MASE)) %>%
  ungroup()
#-------------------------------------------------------------------------------
for (i in 1:3) { # season <- c("A", "M", "N")
  st_best$Additive[i] <- (st_eva %>% filter(ets.s == season[i], ets.t == "A", ets.damp == FALSE) %>% 
                                 top_n(-1, `gmean(MASE)`))$model
  st_best$Damped[i] <- (st_eva %>% filter(ets.s == season[i], ets.t == "A", ets.damp == TRUE) %>% 
                                 top_n(-1, `gmean(MASE)`))$model
  st_best$None[i] <- (st_eva %>% filter(ets.s == season[i], ets.t == "N", ets.damp == FALSE) %>% 
                                 top_n(-1, `gmean(MASE)`))$model
}
st_best
#-------------------------------------------------------------------------------
for (i in 1:3) { # season <- c("A", "M", "N")
  st_acc$Additive[i] <- (st_eva %>% filter(model == "model.select",ets.s == season[i],
                                            ets.t == "A", ets.damp == FALSE))$`gmean(MASE)`
  st_acc$Damped[i] <- (st_eva %>% filter(model == "model.select",ets.s == season[i],
                                          ets.t == "A", ets.damp == TRUE))$`gmean(MASE)`
  st_acc$None[i] <- (st_eva %>% filter(model == "model.select",ets.s == season[i],
                                        ets.t == "N", ets.damp == FALSE))$`gmean(MASE)`
}
st_acc
```

### 6.5 MASE line plot

```{r , echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results='hide'}
acc_fcs <- eva_df %>%
  group_by(horizon, model) %>%
  summarise(MASE = gmean(MASE)) %>%
  mutate(model = ifelse(model == "auto.ari", "auto.arima",
                    ifelse(model == "ets.damp", "damped.ets",
                       ifelse(model == "model.select", "dev.auto.model", model))))
ggplot(acc_fcs, aes(x = horizon, y = MASE, color = model)) + geom_line(size = 0.75) + theme_bw() +
  ggtitle("Average MASE of the developed automatic model across different horizons") +
  theme(plot.title = element_text(size = 10))
```

### 6.6 Example of forecast : M3[[1908]]

```{r , echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results='hide'}
example_series <- 1908
y <- M3[[example_series]]$x
M3[[example_series]]$description # Brick, unglazed (common and face), shipments
M3[[example_series]]$type # INDUSTRY

if ((cv_df %>% filter(series == example_series))$select.flag == 1){
  fit <- ets(y)
} else {
  fit <- auto.arima(y)
}
summary(fit)

# forecast plot
fcast <- forecast:::forecast(fit, h = 18, level = c(80,90,95,99))
plot_fcast <- ggfortify:::fortify.forecast(fcast, ts.connect = TRUE)
ggplot(data = plot_fcast) +
ggtitle("18-month forecast of unglazed brick shipments") +
  xlab("Year") +
  ylab("Amount") +
  geom_line(aes(x= Index, y = Data, color = "Raw data")) +
  geom_line(aes(x= Index, y = Fitted, color = "fitted data")) +
  geom_line(aes(x= Index, y = `Point Forecast`, color = "Forecast")) +
  geom_ribbon(aes(x= Index, ymin = `Lo 99`, ymax = `Hi 99`,  fill = "99%"),  alpha = 0.2) +
  geom_ribbon(aes(x= Index, ymin = `Lo 95`, ymax = `Hi 95`,  fill = "95%"),  alpha = 0.2) +
  geom_ribbon(aes(x= Index, ymin = `Lo 90`, ymax = `Hi 90`,  fill = "90%"),  alpha = 0.25) +
  geom_ribbon(aes(x= Index, ymin = `Lo 80`, ymax = `Hi 80`,  fill = "80%"),  alpha = 0.25) +
  scale_fill_manual("Forecast interval", values = c("#0C1DE8", "#0057FF", "#0C91E8", "#0DDFFF"))+
  scale_color_manual(" ", values = c("red", "blue", "black")) +
  theme_bw()
```